### 2020-08-25 thesis/chap_2.tex
reviewed chap2 intro from Andys comments

\section{Introduction}
%\textit{Problem statement}: Connectivity conservation planning methods do not account for stakeholder perceptions. This can potentially lead to ill-informed conservation plans with low chances of success.
%
%\textit{Research questions}: \textbf{How do different stakeholders perceive connectivity conservation priorities, given the obstacles and opportunities for land use planning apparent in the region, and which conservation scenarios can be derived from these perceptions?} \\

%-----------------------------------------------
% Intro paragraph, similar to that of from chapter 1

The goal of connectivity conservation planning is to preserve the continuity of habitat in a landscape, by identifying and protecting habitat patches and corridors necessary to maintain the movement of plants and animals \citep{keeley_thirty_2019}. Ecological connectivity, defined as the extent to which the landscape facilitates or impedes the movement of organisms \citep{crooks_landscape_2006}, is a critical component of the resilience of populations in heterogeneous and fragmented landscapes \citep{gonzalez_spatial_2017}. Connectivity conservation planning methods do not typically account for, nor confront the perceptions of stakeholders concerning connectivity conservation priorities. Here, we ask how those methods can progress by taking into account those perceptions. To do so, we integrate a connectivity and land use change model (developed in chapter 1) with the results of a community workshop organized with stakeholders, through simple conservation scenarios.

% CCP methods are increasingly Social-Ecological
Conservation planning methods are now recognizing that landscapes constitute social-ecological-systems. A social-ecological system (SES) can be understood as the ensemble of human and non-human actors in a given landscape, the set of natural habitats they inhabit and resources they use, and the set of interactions that are maintained between all the components of the system \citep{ostrom_general_2009}. SESs thus form complex and integrated aggregates of interactions \citep{hinkel_enhancing_2014}. Those interactions also impact governance, the process by which actors in power establish rules and laws \citep{bissonnette_comparing_2018}. To understand a landscape as an SES has important implications for land use planning and therefore for connectivity conservation planning, and pushes connectivity scientists to integrate stakeholder’s perceptions and priorities into their models.

% Why is it important to integrate perceptions
It is important to integrate the perceptions of stakeholders in connectivity planning methods for a multiplicity of reasons. It engages stakeholders in the planning process early on, contributing to better consensus on priorities and, hopefully, to faster action. It also means that connectivity models are enriched by integrating local knowledge into the decision making process, showing that inputs from stakeholders are valued and considered essential to build a conservation plan. More specifically, connectivity conservation is often faced with the issue of understanding the processes driving land use change \citep{worboys_connectivity_2010}. Because land use change is a social process with consequences of both social and ecological nature, questions of land use and connectivity planning cannot be answered without input from stakeholders. Recent studies in land use modeling have shown the value of using stakeholder’s inputs for parameterizing and validating models \citep{hewitt_participatory_2014, voinov_modelling_2010}, leading to a much better understanding of land use processes at play within a landscape.

@@

% Why PM can be beneficial 
Participatory GIS methods such as participatory mapping can allow connectivity conservation models to be more spatially explicit about the obstacles and opportunities presented by connectivity conservation. Understanding how these obstacles and opportunities can influence management decisions is crucial for our understanding of connectivity conservation planning, where land-use conflicts can hinder the protection and restoration of connectivity. Although it is relatively easy to identify where land-use changes might conflict with connectivity conservation, evaluating to which extent these conflicts matter in a local conservation context is more difficult \cite{mitchell_monteregie_2015}.

Here we do not present a scenario design exercise, but a community workshop with a consensus building and participatory mapping exercise, whose results were engineered as simple scenarios in an integrated land use, climate change, and connectivity model (developed in chapter 1). We improve our understanding of the obstacles and opportunities to connectivity conservation in the region, and provide a good starting ground for an iterative process of scenario building. We focused on the region of Montérégie, in southern Quebec, where connectivity conservation has become the focus of land use planning decisions. This project has been developed in collaboration with the non-profit NAQ (Nature action Quebec) in the context of a multi-stakeholder conservation project, the PADF (Plan d’Aménagement Durable des Forêts). The PADF aims at building consensus on priorities for the management and possible conservation of forested land in the region.

% We build on mitchell
This research is pursued in continuation of the project “Monteregie Connection”, whose goal was to engage stakeholders around a discussion of the ecosystem services provided by natural habitat in the region. In the context of this stakeholder-driven project, \cite{mitchell_monteregie_2015} conducted a non-spatially explicit scenario building exercise for a subset of the Monteregie region, the Vallée-de-Richelieu Municipalité Region Comté. The outcome was the 4 scenarios, going from “Periurban Development” to “Green Development”, describing different land use change trends. The Monteregie connection project improved our understanding of the relationship between forest connectivity and ecosystem services. However, there was no effort to estimate the impact of each scenario onto the ecosystem services. This is partially due to a lack of tools able to translate these scenarios into simulations. We contribute to the development of such tools by integrating the results of the workshop into the land use change model developed in chapter 1. The goal of this chapter is therefore twofold: gain a better understanding of conservation priorities in the region, and to provide a basis for an iterative scenario-building process. 
\\
%-----------------------------------------------

>>>>

\section{Introduction}

% Intro paragraph, similar to that of from chapter 1

The goal of connectivity conservation planning is to preserve the continuity of habitat in a landscape, by identifying and protecting habitat patches and corridors necessary to maintain the movement of plants and animals \citep{keeley_thirty_2019}. Ecological connectivity, defined as the extent to which the landscape facilitates or impedes the movement of organisms \citep{crooks_landscape_2006}, is a critical component of the resilience of populations in heterogeneous and fragmented landscapes \citep{gonzalez_spatial_2017}. Connectivity conservation planning methods do not typically account for, nor contrast the perceptions of stakeholders as they relate to  their priorities for conservation. Here, we ask how methods in connectivity conservation can take into account stakeholder perceptions. To do so, we integrate a connectivity and land use change model (developed in chapter 1) with the results of a community workshop organized with stakeholders, through simple conservation scenarios.

Conservation planning methods are now recognizing that landscapes constitute social-ecological-systems. A social-ecological system (SES) can be understood as the ensemble of human and non-human actors in a given landscape, the set of natural habitats they inhabit and resources they use, and the set of interactions that are maintained between all the components of the system \citep{ostrom_general_2009}. SESs thus form complex and integrated aggregates of interactions \citep{hinkel_enhancing_2014}. Those interactions also impact governance, the process by which actors in power establish rules and laws \citep{bissonnette_comparing_2018}. To understand a landscape as an SES has important implications for land use planning and therefore for connectivity conservation planning, and pushes connectivity scientists to integrate stakeholder’s perceptions and priorities into their models.

It is important to integrate the perceptions of stakeholders in connectivity planning methods for a number of reasons. It engages stakeholders in the planning process early on, contributing to better consensus on priorities and, hopefully, to faster action. It also means that connectivity models are enriched by integrating local knowledge into the decision making process, showing that inputs from stakeholders are valued and considered essential to build a conservation plan. More specifically, connectivity conservation is often faced with the issue of understanding the processes driving land use change \citep{worboys_connectivity_2010}. Because land use change is a social process with consequences of both social and ecological nature, questions of land use and connectivity planning cannot be answered without input from stakeholders. Recent studies in land use modelling have shown the value of using stakeholder’s inputs for parameterizing and validating models \citep{hewitt_participatory_2014, voinov_modelling_2010}, leading to a much better understanding of land use processes at play within a landscape.

@@

Participatory GIS methods such as participatory mapping can allow connectivity conservation models to be more spatially explicit about the obstacles and opportunities presented by connectivity conservation. Understanding how these obstacles and opportunities can influence management decisions is crucial for our understanding of connectivity conservation planning, where land-use conflicts can hinder the protection and restoration of connectivity. Although it is relatively easy to identify where land-use changes might conflict with connectivity conservation, evaluating to which extent these conflicts matter in a local conservation context is more difficult \cite{mitchell_monteregie_2015}.

Here, we do not present a scenario design exercise, but a community workshop with a consensus building and participatory mapping exercise, whose results were translated into simple scenarios in an integrated land use, climate change, and connectivity model (developed in chapter 1). We improve our understanding of the obstacles and opportunities to connectivity conservation in the region, and provide a good starting ground for an iterative process of scenario building. We focused on the region of Montérégie, in southern Quebec, where connectivity conservation has become the focus of land use planning decisions. This project has been developed in collaboration with the non-profit NAQ (Nature action Quebec) in the context of a multi-stakeholder conservation project, the PADF (Plan d’Aménagement Durable des Forêts). The PADF aims at building consensus on priorities for the management and possible conservation of forested land in the region.

This research is an extension of the work intitiated by the project “Monteregie Connection”, whose goal was to engage stakeholders around a discussion of the ecosystem services provided by natural habitat in the region. In the context of this stakeholder-driven project, \cite{mitchell_monteregie_2015} conducted a non-spatially explicit scenario building exercise for a subset of the Monteregie region, the Vallée-de-Richelieu Municipalité Region Comté. The outcome was 4 scenarios, ranging from “Periurban Development” to “Green Development”, and each describing different land use change trends. The Monteregie connection project improved our understanding of the relationship between forest connectivity and ecosystem services. However, there was no effort to estimate the impact of each scenario on ecological connectivity. This is partially due to a lack of tools able to translate these scenarios into simulations. We contribute to the development of such tools by integrating the results of the workshop into the land use change model developed in chapter 1. The goal of this chapter is therefore twofold: gain a better understanding of conservation priorities in the region, and to provide a basis for an iterative scenario-building process.

\\
%-----------------------------------------------
